This is the Title

### 2017-02-20 abc/paper/paper.tex
Loads of stuff while sourceforge was down. Installation/hacking notes. Cleanup in dos_execute. Allow globals to have some initializing bytes. During 'optimization', move global initialization to a new initialization stub so that assembly doesn't need to deal with it. Assembling now outputs an initial data segment. Optimize PLUS when arguments are known. New test of globals. Move genvar to cil-util; should rally all variable generation around this struct so that we don't get accidental collisions. Fix a few cases where exceptions were inaccessible because they were generated inside some functor

@@

>>>>

% texticutable

@@

% Literate executable, knuth
% In the dead space of the binary, put this paper or part of it

% ``PISC'' = Printable Instruction Set Computer, etc.

It's a common experience that each time you program a solution to a
hard problem, you do it a different way, due to a lack of complete
satisfaction with the way you did it last time. True to form, the
ABC compiler exercises this technique *within the same compiler*,
using a different approach to represent each of the intermediate
languages.

TODO: Convert byte table thing into ascii. Unfortunately can't fit
the whole 256x256 thing, so maybe 128x128 with a small amount of
cropping, then a 1:1 zoom on the sierpinski triangle part?
